method

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comments

The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015] <!--Tamir, M. (2016). Why do people regulate their emotions? A taxonomy of motives in emotion regulation. Personality and Social Psychology Review, 20(3), 199-222. doi:10.1177/1088868315586325 ;  Tamir, M., Bigman, Y. E., Rhodes, E., Salerno, J., & Schreier, J. (2015). An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making. Emotion, 15(1), 90-103. doi:10.1037/emo0000021  Könnte vor allem das 2. Paper noch hilfreich sein um mehr auf die Values hinzuargumentieren? Ist schon länger her, als ich das gelesen hab. Aber evtl. lohnt es sich, Tamir sagt hier, dass reguliert wird, wenn Personen annehmen, dass die Emotion die sie erzielen möchten, useful ist, also einen Wert hat. Das ist schon anders als die subjective Values, die ihr den ER Strategien zuschreiben möchtet, aber zeigt ja, dass die Analyse von Values im Rahmen von ER als Decision Making schon untersucht wurde, nur eben nicht direkt Values den Strategien zugeschrieben wurde-->.
Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology [@DixonGordon2015;@Lougheed2012;@Southward2018]. 
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
This could be seen as an indirect evidence that subjective effort has an influence on SVs of ER strategies
 <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->

@@

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached. <!-- Hier komme ich noch nicht so ganz mit, könntet ihr das noch klarer beschreiben, was hier passiert? Meint ihr folgendes?: ... The lower monetary value is assigned to different options? oder The lower monetary value is further lowered? Also wird geschaut, wie tief der Wert sein muss, damit die andere Strategie gewählt wird? Sorry, obwohl ihr es schon so oft erklärt habt, bin ich hier immer noch lost, aber das könnte ja anderen Reviewers auch so gehen. Und das die Revs genau in Westbrook schauen, das könnt ihr leider nicht erwarten. -->
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->

>>>>

The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015].
Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology [@DixonGordon2015;@Lougheed2012;@Southward2018]. 
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice[@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
Furthermore, the research on ER choice lacks information regarding the strategies that were *not* chosen in each case.
It is unclear whether people had clear preferences or whether the choice options were similarly attractive.

@@

So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->

### 2022-03-15 06_Paper/ER-ED/method.Rmd
edited comments

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group [@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.

@@

Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of XX participants.
Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).

>>>>

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group [@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).

@@

Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
